Concurrent Priority Queues

### 2014-03-29 presentation/presentation.Rnw
Port slides to Sweave
Various adaptions in RW, Results, etc.

\begin{lstlisting}
bool CAS(T *ptr, T *expected, T value) {
  if (*ptr == *expected) {
    *ptr = value;
    return true;
  } else {
    *expected = *ptr;
    return false;
  }
}
\end{lstlisting}

@@

\item \acp{PQ} in distributed memory systems
    \begin{itemize}
    \item \citeauthor{sanders1998randomized}: Local \acp{PQ}, \lstinline|Insert| at random processor
    \end{itemize}

\item Relaxed data structures
    \begin{itemize}
    \item \citeauthor{kirsch2012fast}: k-FIFO queues
    \end{itemize}

@@

@@

\begin{frame}{\nameref{sec:lockfree}}
\framesubtitle{\citeauthor{sundell2003fast}}
% TODO: Way too much content - skip all except Linden?
\begin{itemize}
\item
\end{itemize}
\end{frame}

@@

\begin{frame}{\nameref{sec:relaxed}}
\framesubtitle{\citeauthor{wimmer2013data}}

\begin{frame}{\nameref{sec:relaxed}}
\framesubtitle{\citeauthor{alistarhspraylist}}

@@

\begin{itemize}
\item All benchmarks were performed on Intel Xeon processors
\item Each thread repeatedly chooses uniformly at random between
      \lstinline|Insert| and \lstinline|DeleteMin|
\item Initial priority queue sizes were $2^{15}$ (Gruber), $10^6$ 
      (\citeauthor{alistarhspraylist}), and unspecified (\citeauthor{linden2013skiplist})
\end{itemize}
\end{frame}

@@

\begin{figure}
% TODO: Sweave
\caption{Throughput benchmark results.}
\end{figure}
\end{frame}

@@

\begin{figure}
\includegraphics[width=0.6 \textwidth]{results_linden}
\caption{Throughput benchmark results.
\emph{New}: \citeauthor{linden2013skiplist},
\emph{HaS}: \citeauthor{shavit2000skiplist},
\emph{SaT}: \citeauthor{sundell2003fast}. 
(Image source: \cite{linden2013skiplist})}
\end{figure}
\end{frame}

\begin{frame}{\nameref{sec:Results}}
\framesubtitle{\citeauthor{alistarhspraylist}}

\begin{figure}
\includegraphics[width=\textwidth]{results_spraylist}
\caption{Throughput benchmark results. 
(Image source: \cite{alistarhspraylist})}
\end{figure}
\end{frame}

>>>>

\begin{lstlisting}
bool CAS(T *ptr, T *expected, T value) {
  if (*ptr == *expected) {
    *ptr = value;
    return true;
  } else {
    *expected = *ptr;
    return false;
  }
}
\end{lstlisting}
\end{frame}

@@

\item Strict \acp{PQ}
    \begin{itemize}
    \item \citeauthor{hunt1996efficient}: \textcolor{BrickRed}{Fine-grained locking heap}
    \item \citeauthor{shavit2000skiplist}: \textcolor{BrickRed}{First SkipList-based \ac{PQ}}
    \item \citeauthor{sundell2003fast}: \textcolor{BrickRed}{First lock-free \ac{PQ}}
    \item \citeauthor{linden2013skiplist}: \textcolor{BrickRed}{Minimizes contention}
    \end{itemize}

\item Relaxed data structures
    \begin{itemize}
    \item \citeauthor{kirsch2012fast}: k-FIFO queues
    \item \citeauthor{wimmer2013data}: \textcolor{BrickRed}{k-\ac{PQ}}
    \item \citeauthor{alistarhspraylist}: \textcolor{BrickRed}{SprayList}
    \end{itemize}

\let\thefootnote\relax\footnote{Highlighted \acp{PQ} are presented in the following}

@@

% TODO: Figure? Whiteboard demo? 1 summary slide only?

@@

\begin{frame}{\nameref{sec:lockfree}}
\framesubtitle{\citeauthor{sundell2003fast}}
% TODO: Short summary only?
\begin{itemize}
\item
\end{itemize}
\end{frame}

\begin{frame}{\nameref{sec:lockfree}}
\framesubtitle{\citeauthor{linden2013skiplist}}
% TODO: Short summary only?
\begin{itemize}
\item
\end{itemize}
\end{frame}

@@

\begin{frame}{\nameref{sec:relaxed}}
\framesubtitle{\citeauthor{alistarhspraylist}}
% Mention that large PQs are required (weak bound)
\begin{itemize}
\item
\end{itemize}
\end{frame}

\begin{frame}{\nameref{sec:relaxed}}
\framesubtitle{\citeauthor{wimmer2013data}}
% Essence: Local list, if necessary push to global
\begin{itemize}
\item
\end{itemize}
\end{frame}

@@

\begin{itemize}
\item Benchmarking results from selected papers \& own results
\item Each thread repeatedly chooses uniformly at random between
      \lstinline|Insert| and \lstinline|DeleteMin|
\item We present throughput, i.e. the number of operations performed per second
\end{itemize}
\end{frame}

@@

\begin{figure}
<<results = tex, echo = FALSE>>=
\SweaveInput{../common/pqplot.Rnw}
pqplot("../results/results.csv")
@
\caption{GCC 4.8.2, 80-core Intel Xeon E7-8850 @ 2.0 GHz. \ac{PQ} initialized with $2^{15}$
elements.}
\end{figure}
\end{frame}

@@

\begin{figure}
\includegraphics[width=0.6 \textwidth]{results_linden}
\caption{GCC 4.7.2, 32-core Intel Xeon E5-4650 @ 2.7 GHz. Initial \ac{PQ} size unknown.
\emph{New}: \citeauthor{linden2013skiplist},
\emph{HaS}: \citeauthor{shavit2000skiplist},
\emph{SaT}: \citeauthor{sundell2003fast}. 
(Image source: \cite{linden2013skiplist})}
\end{figure}
\end{frame}

\begin{frame}{\nameref{sec:Results}}
\framesubtitle{\citeauthor{alistarhspraylist}}
% 10^6
\begin{figure}
\includegraphics[width=\textwidth]{results_spraylist}
\caption{GCC version unknown, 80-core Intel Xeon E7-4870 @ 2.4 GHz. \ac{PQ} initialized with $10^6$
elements.
(Image source: \cite{alistarhspraylist})}
\end{figure}
\end{frame}
